|

### 2022-12-02 paper_comparison/paper_comparison/paper_comparison.Rmd
removed landscape mode
update conventional simulation (RESET test)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = es,
                            F_p_value = mod$test(tmp_dat)$p_value,
                            BP_p_value = HETER_MODEL$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

@@

                     tibble(a = a,
                            b = b,
                            x_dist = x_dist,
                            n = n,
                            effect_size = es,
                            F_p_value = POLY_MODEL$test(mutate(tmp_dat, z = poly_model()$gen(n, computed = select(tmp_dat, x))$z))$p_value,
                            BP_p_value = mod$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

@@

```{r dataplotsel, fig.cap = "..."}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            weighted_detect = sum(weighted_detect),
            n_eval = n()) %>%
  group_by(plot_p_value_rank) %>%
  summarise(weighted_detect = sum(weighted_detect),
            n_eval = sum(n_eval)) %>%
  ggplot() +
  geom_col(aes(factor(plot_p_value_rank), n_eval)) +
  geom_col(aes(factor(plot_p_value_rank), weighted_detect, fill = "weighted number of detections")) +
  xlab("Data plot p-value rank") +
  ylab("Number of Lineups") +
  theme(legend.position = "bottom") +
  labs(fill = "")
```

```{r dadtaplotselfacet, fig.cap = "..."}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  left_join(vi_survey_with_plot %>%
              filter(!attention_check) %>%
              filter(!null_lineup) %>%
              filter(answer == plot) %>%
              group_by(unique_lineup_id) %>%
              summarise(answer_rank = first(plot_p_value_rank))) %>%
  mutate(weighted_sel = ifelse(num_selection == 0, 0.05, plot_sel/num_selection)) %>%
  group_by(plot_p_value_rank, answer_rank) %>%
  summarise(weighted_sel = sum(weighted_sel)) %>%
  ggplot() +
  geom_col(aes(factor(plot_p_value_rank), weighted_sel)) +
  geom_vline(data = data.frame(answer_rank = 1:20, x = 1:20),
             aes(xintercept = x),
             col = "red") +
  facet_wrap(~answer_rank, scales = "free_y") +
  xlab("Plot p-value rank") +
  ylab("Weighted number of selections")
```

>>>>

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = es,
                            F_p_value = mod$test(tmp_dat)$p_value,
                            RESET_p_value = mod$test(tmp_dat, test = "RESET", power = 2:3, power_type = "fitted")$p_value,
                            BP_p_value = HETER_MODEL$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

@@

                     tibble(a = a,
                            b = b,
                            x_dist = x_dist,
                            n = n,
                            effect_size = es,
                            F_p_value = POLY_MODEL$test(mutate(tmp_dat, z = poly_model()$gen(n, computed = select(tmp_dat, x))$z))$p_value,
                            RESET_p_value = POLY_MODEL$test(tmp_dat, test = "RESET", power = 2:3, power_type = "fitted")$p_value,
                            BP_p_value = mod$test(tmp_dat)$p_value,
                            SW_p_value = shapiro.test(tmp_dat$.resid)$p.value,
                            boot_id = i)
                   }) %>%
  reduce(bind_rows)
  }

@@

```{r dataplotsel, fig.cap = "..."}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            weighted_detect = sum(weighted_detect),
            n_eval = n()) %>%
  group_by(plot_p_value_rank) %>%
  summarise(weighted_detect = sum(weighted_detect),
            n_eval = sum(n_eval)) %>%
  mutate(plot_p_value_rank_g5 = plot_p_value_rank >= 5) %>%
  group_by(plot_p_value_rank_g5) %>%
  mutate(n_eval = ifelse(plot_p_value_rank_g5, sum(n_eval), n_eval)) %>%
  mutate(weighted_detect = ifelse(plot_p_value_rank_g5, sum(weighted_detect), weighted_detect)) %>%
  ungroup() %>%
  filter(plot_p_value_rank <= 5) %>%
  mutate(plot_p_value_rank = ifelse(plot_p_value_rank == 5, "5+", as.character(plot_p_value_rank))) %>%
  mutate(plot_p_value_rank = factor(plot_p_value_rank, levels = c(as.character(1:5), "5+"))) %>%
  ggplot() +
  geom_col(aes(plot_p_value_rank, n_eval)) +
  geom_col(aes(plot_p_value_rank, weighted_detect, fill = "weighted number of detections")) +
  xlab("Data plot p-value rank") +
  ylab("Number of Lineups") +
  theme(legend.position = "bottom") +
  labs(fill = "")
```

```{r dadtaplotselfacet, fig.cap = "...", fig.height=12, fig.width=16}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(type == "polynomial") %>%
  left_join(vi_survey_with_plot %>%
              filter(!attention_check) %>%
              filter(!null_lineup) %>%
              filter(answer == plot) %>%
              group_by(unique_lineup_id) %>%
              summarise(answer_rank = first(plot_p_value_rank))) %>%
  mutate(weighted_sel = ifelse(num_selection == 0, 0.05, plot_sel/num_selection)) %>%
  group_by(plot_p_value_rank, answer_rank) %>%
  summarise(weighted_sel = sum(weighted_sel)) %>%
  mutate(answer_rank_g5 = answer_rank >= 5) %>%
  group_by(plot_p_value_rank, answer_rank_g5) %>%
  mutate(weighted_sel = ifelse(answer_rank_g5, sum(weighted_sel), weighted_sel)) %>%
  ungroup() %>%
  filter(answer_rank <= 5) %>%
  mutate(answer_rank = ifelse(answer_rank == 5, "5+", as.character(answer_rank))) %>%
  mutate(answer_rank = factor(answer_rank, levels = c(as.character(1:5), "5+"))) %>%
  ggplot() +
  geom_col(aes(factor(plot_p_value_rank), weighted_sel)) +
  geom_vline(data = data.frame(answer_rank = c("1", "2", "3", "4"), x = 1:4),
             aes(xintercept = x),
             col = "red") +
  facet_wrap(~answer_rank, scales = "free_y") +
  xlab("Plot p-value rank") +
  ylab("Weighted number of selections")
```

```{r eval = FALSE}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            weighted_detect = sum(weighted_detect),
            n_eval = n(),
            reject = first(conventional_p_value < 0.05)) %>%
  group_by(plot_p_value_rank, reject) %>%
  summarise(weighted_detect = sum(weighted_detect),
            n_eval = sum(n_eval)) %>%
  ggplot() +
  geom_col(aes(factor(plot_p_value_rank), n_eval)) +
  geom_col(aes(factor(plot_p_value_rank), weighted_detect, fill = "weighted number of detections")) +
  xlab("Data plot p-value rank") +
  ylab("Number of Lineups") +
  theme(legend.position = "bottom") +
  labs(fill = "") +
  facet_wrap(~reject)
```
